Joshua 2.0: A Toolkit for Parsing-Based Machine Translation \\with Syntax, Semirings, Discriminative Training and Other Goodies

### 2010-04-23 papers/wmt10/joshua-progress.tex
Edited Anni's section
git-svn-id: https://joshua.svn.sourceforge.net/svnroot/joshua/branches/publications@1632 0ae5e6b2-d358-4f09-a895-f82f13dd62a4

Integrating output from specialized modules (like transliterators, morphological analyzers, and modality translators) into the MT pipeline can improve translation performance, particularly in low-resource settings. We have implemented this functionality in Joshua by supporting an XML format for proposing alternate translation rules (constraints) for a particular word span to the decoder \cite{PBML-2010-Joshua-modules}. That is, processing that is separate from the MT engine can suggest translations for some set of source side words and phrases. The XML format allows for both hard constraints, which must be used, and soft constraints, which compete with standard extracted translation rules, as well as specifying associated feature weights. We modified the chart-based decoder to support these constraints.

>>>>

Integrating output from specialized modules (like transliterators, morphological analyzers, and modality translators) into the MT pipeline can improve translation performance, particularly for low-resource languages. We have implemented an XML interface that allows external modules to propose alternate translation rules (constraints) for a particular word span to the decoder \cite{PBML-2010-Joshua-modules}. Processing that is separate from the MT engine can suggest translations for some set of source side words and phrases. The XML format allows for both hard constraints, which must be used, and soft constraints, which compete with standard extracted translation rules, as well as specifying associated feature weights. Additionally the XML format allows constraints on the righthand side of SCFG rules, which allows constraints like forcing a particular span to be a NP.  We modified the chart-based decoder to support these constraints.
